---
title       : Multivariate Linear Models for mtcars Dataset
subtitle    : Developing Data Products - Course Project
author      : Reinald Kim T. Amplayo
job         : Coursera Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Product Inspiration

- Course Project of Regression Models class
- Makes use of the mtcars dataset
- You create a linear model that has the transmission (am) variable as a predictor and the mpg variable as an outcome
- You interpret the variables correctly and quantify the difference between the two types of transmission in terms of their mpg
- This product helps you answer that course project!

---

## About the mtcars Dataset

- Motor Trend Car Road Tests
- The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r echo=FALSE, cache=TRUE}
str(mtcars)
```

---

## How to Use the Product

1. Choose a combination of features/variables by checking boxes
2. Look at the output, especially the R^2 and the P-values of each variables
3. To check if a feature is helpful, make a plot by choosing a feature and plot it with mpg
4. Go back to 1. until you are satisfied!  

- Very easy! Right?

---

## Next Version Announcements

- We will include multiple datasets, not just mtcars!
- We will include interactions between features! For example, this will be supported, which makes better regression models:

```{r echo=FALSE, cache=TRUE}
summary(lm(mpg ~ hp + am + qsec + qsec:hp + am:wt, mtcars))$coefficients
summary(lm(mpg ~ hp + am + qsec + qsec:hp + am:wt, mtcars))$r.squared
```

- Thank you!